Checklist

### 2017-08-01 presentations/2017-08-02_shutdown/checklist.tex
[presentations/2017-08-02_shutdown] Format update and include location notes

\documentclass[10pt,fleqn,twocolumn]{article}
% \usepackage[journal=rsc]{chemstyle}
% \usepackage{mhchem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{esint}
\usepackage{bbm}
\usepackage{amscd}
\usepackage{picinpar}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tikz-3dplot}
\usepackage{indentfirst}
\usepackage{wrapfig}
\usepackage{units}
\usepackage{textcomp}
\usepackage[utf8x]{inputenc}
% \usepackage{feyn}
\usepackage{feynmp}
\usepackage{xkeyval}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage{pgfplots}
\usepackage{hyperref}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes
}

\DeclareGraphicsRule{*}{mps}{*}{}
\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\eqar}[1]
{
  \begin{align*}
    #1
  \end{align*}
}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{fontenc}
% \usepackage{tipa}
\usepackage{ulem}
\usepackage{color}
\usepackage{cancel}
\newcommand{\hcancel}[2][black]{\setbox0=\hbox{#2}%
  \rlap{\raisebox{.45\ht0}{\textcolor{#1}{\rule{\wd0}{1pt}}}}#2}
\pagestyle{fancy}
\setlength{\headheight}{67pt}
\fancyhead{}
\fancyfoot{}
\fancyfoot[C]{\thepage}
\fancyhead[R]{}
\renewcommand{\footruleskip}{0pt}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

@@

\newcommand\DevDef[2]{
  \begin{minipage}{\linewidth}
    \begin{itemize}
    \item\DevHeader{#1}
      #2
    \end{itemize}
    \vspace{0.8cm}
  \end{minipage}
}
\newcommand\Person[1]{
\clearpage
\section*{#1}
\fancyhead[R]{#1}
\setcounter{page}{1}
\setcounter{subsection}{0}
For shutting off, go through the checklist in the following order
\begin{itemize}
\item\OffBox Turn off equipments
\item\OffBox Turn off power supplies
\item\OffBox Turn off computers
\end{itemize}
Wait before everyone else finish their corresponding steps before starting the next one.\\
For powering up, go through the checklist in the following order
\begin{itemize}
\item\OnBox Turn on computers
\item\OnBox Turn on power supplies
\item\OnBox Turn on equipments
\item\OnBox Check computer connection to devices
\end{itemize}
Also wait before everyone else finish their corresponding steps before starting the next one.
}
\renewcommand{\thesubsection}{\arabic{subsection}}

@@

\Person{Yichao}
\subsection{Equipments}
\DevDef{Thorlabs temperature controller for Na Raman doubler}{
  \textbf{1st level above Na Raman and D2 seed lasers}\\
  Record temperature settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{Computer control box for 1.0}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the front side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply.
  \item\OnBox Turn on the power switch of the box. The fans should start spinning.
  \end{itemize}
}
\Person{Jon}
\subsection{Equipments}
\DevDef{Agilent function generator for Na 1.0 switching}{
  \textbf{1st level above TiSapph facing computers}\\
  Record parameters:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{Tweezer 2 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Andor camera
  \end{itemize}
}
\DevDef{Tweezer 3 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Software radio
  \end{itemize}
}
\Person{Lee}
\subsection{Equipments}
\DevDef{PLL for 1.0 Cs MOT}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
  \end{itemize}
}
\DevDef{PLL for 1.0 Cs Raman}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
  \end{itemize}
}
\DevDef{Homebuilt temperature servo for Cs 1.0 MOT}{
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Switch off/on the front switch
}
\DevDef{1st version Till's current controller for Cs MOT}{
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Record current value:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{Tweezer 1 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Thorlabs cameras
  \item\OnBox Na Raman amplifier
  \end{itemize}
}
\Person{Jessie}
\subsection{Equipments}
\DevDef{TiSapph}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off pump, unplug from wall
  \item\OffBox Turn off controller, unplug from wall
  \item\OffBox Turn off chiller, unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall, turn on chiller
  \item\OnBox Plug into wall, turn on controller
  \item\OnBox Plug into wall, turn on pump
  \end{itemize}
}
\DevDef{Quantel Laser}{
  \textbf{1st level in the middle, facing 1.5 table}\\
  Ask Frederic.
  \vspace{1cm}
}
\DevDef{Intensity servo for Na}{
  \textbf{1st level above Na tweezer, below 1.0 computer control box}\\
  Unplug power
}
\DevDef{1st version Till's current controller for butterfly laser}{
  \textbf{1st level above TiSapph}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
}
\DevDef{Homebuilt temperature servo for butterfly laser}{
  \textbf{1st level above TiSapph}\\
  Switch off/on the front switch
}
\DevDef{PLL for 1.5 Cs MOT}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings ???
  \end{itemize}
}
\subsection{Power supplies}
\DevDef{Homebuilt $24$V power supply}{
  \textbf{2nd level above NaCs 1.0 chamber, facing the drawers/wall}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply for dispensers}{
  \textbf{1st level above NaCs 1.0 chamber}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply for 1.5 computer control clock}{
  \textbf{2nd level next to 1.5 computer control box}\\
  Record voltage/current values:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Homebuilt $\pm15,5$V power supply}{
  \textbf{2nd level above TiSapph}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{Computer control box for 1.5}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the left side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply. The fans should start spinning.
  \item\OnBox Turn on the power switch of the box.
  \end{itemize}
}
\Person{Frederic}
\subsection{Equipments}
\DevDef{Andor Camera for 1.5}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Switch off
  \item\OffBox Switch off chiller
  \item\OffBox Unplug camera power (zip tie to camera)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in camera power
  \item\OnBox Switch on chiller
  \item\OnBox Switch on
  \end{itemize}
}
\DevDef{1.5 Feshbach coils}{
  \textbf{Before power shutdown}
  \begin{itemize}
  \item\OffBox Wrap exposed part in napkins to prevent condensations
  \end{itemize}
}
\DevDef{1.5 IGBT}{
  \textbf{Before power shutdown}
  \begin{itemize}
  \item\OffBox Wrap exposed part in napkins to prevent condensations
  \end{itemize}
}
\DevDef{Cooling water}{
  Valves to close/reopen:\\

>>>>

\documentclass[10pt,fleqn,twocolumn]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{esint}
\usepackage{bbm}
\usepackage{amscd}
\usepackage{picinpar}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tikz-3dplot}
\usepackage{indentfirst}
\usepackage{wrapfig}
\usepackage{units}
\usepackage{textcomp}
\usepackage[utf8x]{inputenc}
% \usepackage{feyn}
\usepackage{feynmp}
\usepackage{xkeyval}
\usepackage{xargs}
\usepackage{verbatim}
\usepackage{pgfplots}
\usepackage{hyperref}
\usetikzlibrary{
  arrows,
  calc,
  decorations.pathmorphing,
  decorations.pathreplacing,
  decorations.markings,
  fadings,
  positioning,
  shapes
}

\DeclareGraphicsRule{*}{mps}{*}{}
\newcommand{\ud}{\mathrm{d}}
\newcommand{\ue}{\mathrm{e}}
\newcommand{\ui}{\mathrm{i}}
\newcommand{\res}{\mathrm{Res}}
\newcommand{\Tr}{\mathrm{Tr}}
\newcommand{\dsum}{\displaystyle\sum}
\newcommand{\dprod}{\displaystyle\prod}
\newcommand{\dlim}{\displaystyle\lim}
\newcommand{\dint}{\displaystyle\int}
\newcommand{\fsno}[1]{{\!\not\!{#1}}}
\newcommand{\eqar}[1]
{
  \begin{align*}
    #1
  \end{align*}
}
\newcommand{\texp}[2]{\ensuremath{{#1}\times10^{#2}}}
\newcommand{\dexp}[2]{\ensuremath{{#1}\cdot10^{#2}}}
\newcommand{\eval}[2]{{\left.{#1}\right|_{#2}}}
\newcommand{\paren}[1]{{\left({#1}\right)}}
\newcommand{\lparen}[1]{{\left({#1}\right.}}
\newcommand{\rparen}[1]{{\left.{#1}\right)}}
\newcommand{\abs}[1]{{\left|{#1}\right|}}
\newcommand{\sqr}[1]{{\left[{#1}\right]}}
\newcommand{\crly}[1]{{\left\{{#1}\right\}}}
\newcommand{\angl}[1]{{\left\langle{#1}\right\rangle}}
\newcommand{\tpdiff}[4][{}]{{\paren{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}_{#4}}}
\newcommand{\tpsdiff}[4][{}]{{\paren{\frac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pdiff}[3][{}]{{\frac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\diff}[3][{}]{{\frac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psdiff}[3][{}]{{\frac{\partial^{#1}}{\partial {#3}{}^{#1}} {#2}}}
\newcommand{\sdiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\newcommand{\tpddiff}[4][{}]{{\left(\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}\right)_{#4}}}
\newcommand{\tpsddiff}[4][{}]{{\paren{\dfrac{\partial^{#1}}{\partial {#3}{}^{#1}}{#2}}_{#4}}}
\newcommand{\pddiff}[3][{}]{{\dfrac{\partial^{#1} {#2}}{\partial {#3}{}^{#1}}}}
\newcommand{\ddiff}[3][{}]{{\dfrac{\ud^{#1} {#2}}{\ud {#3}{}^{#1}}}}
\newcommand{\psddiff}[3][{}]{{\frac{\partial^{#1}}{\partial{}^{#1} {#3}} {#2}}}
\newcommand{\sddiff}[3][{}]{{\frac{\ud^{#1}}{\ud {#3}{}^{#1}} {#2}}}
\usepackage{fancyhdr}
\usepackage{multirow}
\usepackage{fontenc}
\usepackage{titlesec}
% \usepackage{tipa}
\usepackage{ulem}
\usepackage{color}
\usepackage{cancel}

\newcommand{\hcancel}[2][black]{\setbox0=\hbox{#2}%
  \rlap{\raisebox{.45\ht0}{\textcolor{#1}{\rule{\wd0}{1pt}}}}#2}
\pagestyle{fancy}
% \setlength{\headheight}{60pt}
\fancyhead{}
\fancyfoot{}
\fancyfoot[C]{\thepage}
\fancyhead[R]{}
\renewcommand{\footruleskip}{0pt}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}
\titlespacing{\subsection}{0pt}{\parskip}{-\parskip}

@@

\newcommand\DevDef[2]{
  \begin{minipage}[t]{\linewidth}
    \begin{itemize}
    \item\DevHeader{#1}
      #2
    \end{itemize}
    \vspace{0.8cm}
  \end{minipage}
}
\newcommand\Person[1]{
\clearpage
\section*{#1}
\fancyhead[R]{#1}
\setcounter{page}{1}
\setcounter{subsection}{0}
For shutting off, go through the checklist in the following order
\begin{itemize}
\item\OffBox Turn off equipments
\item\OffBox Turn off power supplies
\item\OffBox Turn off computers
\end{itemize}
Wait before everyone else finish their corresponding steps before starting the next one.\\
For powering up, go through the checklist in the following order
\begin{itemize}
\item\OnBox Turn on computers
\item\OnBox Turn on power supplies
\item\OnBox Turn on equipments
\item\OnBox Check computer connection to devices
\end{itemize}
Also wait before everyone else finish their corresponding steps before starting the next one.\\

}
\renewcommand{\thesubsection}{\arabic{subsection}}

@@

\Person{Yichao}
\textbf{\Large
  Equipments and power supplies are mostly located around the laser table on the library side.
}\\
\subsection{Equipments}
\DevDef{Thorlabs temperature controller for Na Raman doubler}{
  \textbf{1st level above Na Raman and D2 seed lasers}\\
  Record temperature settings\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{UPS}{
  \textbf{2nd level above laser table}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on
  \end{itemize}
}
\subsection{Computers}
\DevDef{Computer control box for 1.0}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the front side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply.
  \item\OnBox Turn on the power switch of the box. The fans should start spinning.
  \end{itemize}
}
\Person{Jon}
\textbf{\Large
  Equipments and power supplies are mostly located around the machine table facing the laser table
  or the computer area.
}\\
\subsection{Equipments}
\DevDef{Agilent function generator for Na 1.0 switching}{
  \textbf{1st level above TiSapph facing computers}\\
  Record parameters:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{Tweezer 2 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Andor camera
  \end{itemize}
}
\DevDef{Tweezer 3 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Software radio
  \end{itemize}
}
\Person{Lee}
\textbf{\Large
  Equipments and power supplies are mostly located around the laser table
  on the computer area side.
}\\
\subsection{Equipments}
\DevDef{PLL for 1.0 Cs MOT}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
  \end{itemize}
}
\DevDef{PLL for 1.0 Cs Raman}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings according to note on Generic tab, Equipment Settings.
  \end{itemize}
}
\DevDef{Homebuilt temperature servo for Cs 1.0 MOT}{
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Switch off/on the front switch
}
\DevDef{1st version Till's current controller for Cs MOT}{
  \textbf{1st level above Cs tweezer/MOT lasers}\\
  Record current value:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{Tweezer 1 computer}{
  \textbf{Check following devices}
  \begin{itemize}
  \item\OnBox Thorlabs cameras
  \item\OnBox Na Raman amplifier
  \end{itemize}
}
\Person{Jessie}
\textbf{\Large
  Equipments and power supplies are mostly located around the machine table facing the 1.5 table.
}\\
\subsection{Equipments}
\DevDef{TiSapph}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off pump, unplug from wall
  \item\OffBox Turn off controller, unplug from wall
  \item\OffBox Turn off chiller, unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into wall, turn on chiller
  \item\OnBox Plug into wall, turn on controller
  \item\OnBox Plug into wall, turn on pump
  \end{itemize}
}
\DevDef{Quantel Laser}{
  \textbf{1st level in the middle, facing 1.5 table}\\
  Ask Frederic.
  \vspace{1cm}
}
\DevDef{Intensity servo for Na}{
  \textbf{1st level above Na tweezer, below 1.0 computer control box}\\
  Unplug power
}
\DevDef{1st version Till's current controller for butterfly laser}{
  \textbf{1st level above TiSapph}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Turn off
  \item\OffBox Unplug power (zip tie to controller)
  \end{itemize}
}
\DevDef{Homebuilt temperature servo for butterfly laser}{
  \textbf{1st level above TiSapph}\\
  Switch off/on the front switch
}
\DevDef{PLL for 1.5 Cs MOT}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug all signals (zip tie together)
  \item\OffBox Unplug 15V and 5V powers (zip tie together)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plugin 15V and 5V powers
  \item\OnBox Plugin all signals
  \item\OnBox Apply settings ???
  \end{itemize}
}
\subsection{Power supplies}
\DevDef{Homebuilt $24$V power supply}{
  \textbf{2nd level above NaCs 1.0 chamber, facing the drawers/wall}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply for dispensers}{
  \textbf{1st level above NaCs 1.0 chamber}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Benchtop power supply for 1.5 computer control clock}{
  \textbf{2nd level next to 1.5 computer control box}\\
  Record voltage/current values:\\

@@

  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug loads
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Turn off the power supply
  \item\OffBox Unplug from wall
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug into the wall
  \item\OnBox Turn on the power supply \textbf{Do NOT do this with loads pluged in}
  \item\OnBox Plug the load back in
  \end{itemize}
}
\DevDef{Homebuilt $\pm15,5$V power supply}{
  \textbf{2nd level above TiSapph}\\
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Unplug load
  \item\OffBox Label and zip tie loads to the power supply
  \item\OffBox Switch off on the back
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Switch on
  \item\OnBox Plug the load back in
  \end{itemize}
}
\subsection{Computers}
\DevDef{Computer control box for 1.5}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox (Do following three steps quickly)
  \item\OffBox Turn off the box by flipping the switch on the front side of the box
  \item\OffBox Unplug the high voltage (48V) power supply (circular plug)
    on the left side of the box. Then unplug the power supply itself fromm the outlet.
  \item\OffBox Unplug the 12V board power supply.
    (L.T.E. one with a rectangular connector in the front)
  \item\OffBox Unplug USB power on the front side near the fan.
  \item\OffBox Zip tie the three unpluged powers to the computer control box.
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Connect to 3.5G Windfrek clock generator from Tweezer1.
    Set frequency to 3.5G and amplitude to max.
  \item\OnBox (Remove power connection zip ties and) Plug in USB power supply.
  \item\OnBox (Do following three steps quickly)
  \item\OnBox Plug in the 12V board power supply.
  \item\OnBox Plug in high voltage power supply. The fans should start spinning.
  \item\OnBox Turn on the power switch of the box.
  \end{itemize}
}
\Person{Frederic}
\textbf{\Large
  Equipments and power supplies are mostly on the 1.5 rack.
}\\
\subsection{Equipments}
\DevDef{Andor Camera for 1.5}{
  \textbf{Turn off check list}
  \begin{itemize}
  \item\OffBox Switch off
  \item\OffBox Switch off chiller
  \item\OffBox Unplug camera power (zip tie to camera)
  \end{itemize}
  \textbf{Turn on check list}
  \begin{itemize}
  \item\OnBox Plug in camera power
  \item\OnBox Switch on chiller
  \item\OnBox Switch on
  \end{itemize}
}
\DevDef{1.5 Feshbach coils}{
  \textbf{Before power shutdown}
  \begin{itemize}
  \item\OffBox Wrap exposed part in napkins to prevent condensations
  \end{itemize}
}
\DevDef{1.5 IGBT}{
  \textbf{Before power shutdown}
  \begin{itemize}
  \item\OffBox Wrap exposed part in napkins to prevent condensations
  \end{itemize}
}
\DevDef{Cooling water}{
  Valves to close/reopen:\\
